\begin{center}
\thispagestyle{empty}
\vspace{2cm}
\LARGE{\textbf{Abstract}}\\[1.0cm]
\end{center}
\large{\paragraph{} Today the automated guided vehicle (AGV) plays an important role in the design and growth of new factories and warehouses. Automated Guided vehicle (AGV) is a robot that follows markers or wires in the floor or uses vision or lasers for navigation and used to transfer load from one position to another. The basic functions of AGV are navigation and load transfer in industries or warehouses.In an automated process, AGVs are programmed to communicate with other robots to ensure the product is moved smoothly through the warehouse, whether it is being stored for future use or sent directly to shipping areas.
}
\large{\paragraph{}. As per increasing technologies, industries lack adaptive AGVs. That means, AGVs with constant hardware and software upgrades. Lack of vision-based navigation in the AGVs, make them single task-oriented. So, here we are proposing the advanced version of machine vision-based smart automated guided vehicle which incorporates the ML algorithm and would be beneficial for predicting the failures/problem before time and increasing task efficiency and accuracy. The proposed AGV also contains self-charging and can predict the possible future working hours of it. This adaptive AGV is low-cost since it must eventually attract more industries from various fields. Deploying it for repetitive material handling tasks can also allow enterprises to save on labor costs and reassign staff on other essential tasks, such as enhancing customer satisfaction. }\\

\textbf{Keywords: }Automated Guided vehicle, AGV, Wireless, Machine vision, ML, IoT, Shortest Path Algorithm, Side Arm, Robotics Arm, Autonomous, Industries, Hospitals