\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{}
\small

\bibitem{KHyyppa} Kalevi Hyypp\"{a}, ``Method of Navigating an Automated Guided Vehicle", Patent No. 4,811,228, United States Patent, Mar. 7, 1989

\bibitem{RArkin} Ronald C. Arkin, Robin R. Murphy, ``Autonomous Navigation in a Manufacturing Environment", IEEE Transaction on Robotics and Automation, Vol. 6, No. 4, pp.445-454, 1990

\bibitem{BMahadevan} B. Mahadevan, T. T. Narendran, ``Design of an automated guided vehicle-based material handling system for a flexible manufacturing system", International Journal of Production Research, Vol. 28, No. 9, pp. 1611-1622, 1990

\bibitem{WGoetz} William G. Goetz, Jr, Pius J. Egbelu, ``Guide path design and location of load pick-up/drop-off points for an automated guided vehicle system", International Journal of Production Research, Vol. 28, No. 5, pp. 927-941, 1990

\bibitem{SArora} Sudha Arora, A. K. Raina, A. K. Mittal, ``Collision Avoidance among AGVs at Junctions", Proceedings of the IEEE Intelligent Vehicles Symposium, pp. 585-589, 2000

\bibitem{NWinters} Niall Winters, Jos\'{e} Gaspar, Gerard Lacey, Jos\'{e}, Santos-Victor, ``Omni-directional Vision for Robot Navigation", Proceedings IEEE Workshop on Omnidirectional Vision, 2000

\bibitem{TFujimoto} T. Fujimoto, J. Ota, T. Arai, T. Ueyama, T. Nishiyama, ``Semi-guided navigation of AGV through iterative learning", Proceedings 2001 IEEE/RSJ International Conference on Intelligent Robots and Systems, pp. 968-973, 2001

\bibitem{DZeitler} David W. Zeitler, Andrew R. Black, Clyde Miin-Arng Ko, ``Automated Guided Vehicle (AGV) with BiPolar Magnet Sensing", US 6,345,217 B1, United States Patent and Trademark Office, Feb. 5, 2002

\bibitem{SSkaff} Sarjoun Skaff, George Kantor, David Maiwand, Alfred A. Rizzi, ``Inertial Navigation and Visual Line Following for a Dynamical Hexapod Robot", 2003 IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), Vol. 2, pp. 1808-1813, 2003 

\bibitem{QFang} Qiang Fang, Cunxi Xie, ``A Study on Intelligent Path Following and Control for Vision-based Automated Guided Vehicle", 5$^{th}$ World Congress on Intelligent Control and Automation, pp. 4811-4815, 2004


\bibitem{HZhang} Hai-Bo Zhang, Kui Yuan, Shu-Qi Mei, Qing-Rui Zhou, ``Visual Navigation of an Automated Guided Vehicle based on Path Recognition", Third International Conference on Machine Learning and Cybernetics, pp. 3877-3881, 2004

\bibitem{RRojas} Ra\'{u}l Rojas, Alexander F\"{o}rster, ``Holonomic Control of a robot with an omni-directional drive'', K\"{u}nstliche Intelligenz, B\"{o}ttcherIT Verlag, 2006 

\bibitem{Iris} Iris F. A., Vis, ``Survey of research in the design and control of automated guided vehicle systems", European Journal of Operational Research, Volume 170, Issue 3, pp. 677-709, 2006

\bibitem{CLozoya} C. Lozoya, P. Martí, M. Velasco, J.M. Fuertes, ``Effective Real-Time Wireless Control of an Autonomous Guided Vehicle", 2007 IEEE International Symposium on Industrial Electronics, pp. 2876-2881, 2007

\bibitem{HBarbera} H. Mart\'{i}nez-Barber\'{a}, D. Herrero-P\'{e}rez, ``Autonomous navigation of an automated guided vehicle in industrial environments", Robotics and Computer-Integrated Manufacturing, Vol. 26, pp. 296-311, 2009 

\bibitem{ZCao} Zuoliang Cao, Yanbin Li, Shenghua Ye, ``Omni-directional vision sensor for mobile robot navigation based on particle filter", Robot Localization and Map Building, pp. 349-364, 2010

\bibitem{NIsozaki} Naoya Isozaki, Daisuke Chugo, Sho Yokota, Kunikatsu Takase, ``Camera-based AGV Navigation System for Indoor Environment with Occlusion Condition", IEEE International Conference on Mechatronics and Automation, pp. 778-783, 2011

\bibitem{RPiyare} Rajeev K Piyare, Ravinesh Singh, ``Wireless Control of an Automated Guided
Vehicle", International MultiConference of Engineers and Computer Scientists(IMECS), Vol II, pp. 828-833, 2011

\bibitem{AYe} Aixue Ye, Haibing Zhu, Zhengdong Xu,Chenxi Sun, Kui Yuan, ``A Vision-Based Guidance Method for Autonomous Guided Vehicles", of 2012 IEEE International Conference on Mechatronics and Automation, pp. 2025-2030, 2012

\bibitem{KKumar} K. Kishore Kumar, M. Siva Krishna, D. Ravitej, D. Bhavana, ``Design of Automatic Guided Vehicle", International Journal of Mechanical Engineeringa and Technology (IJMET), Vol. 3, Issue 1, pp. 24-32, 2012

\bibitem{QVan} Quan Nguyen Van, Hyuk-Min Eum, Jeisung Lee, Chang-Ho Hyun, ``Vision Sensor-Based Driving Algorithm for Indoor Automatic Guided Vehicles", International Journal of Fuzzy Logic and Intelligent Systems, Vol. 13, No. 2, pp. 140-146, 2013

\bibitem{WElhady} Walaa E. Elhady, Heba A. Elnemr, Gamal Selim, ``Implementation and Evaluation of Image Processing on Vision Navigation Line Follower Robot", Journal of Computer Science, pp. 1036-1044, 2014

\bibitem{JLopez} Joaquin L\'{o}pez, Diego P\'{e}rez, Iago Vaamonde, Enrique Paz, Alba Vaamonde, Jorge Cabaleiro, ``Building a Warehouse Control System using RIDE", Robot 2015: Second Iberian Robotics Conference - Advances in Robotics, Lisbon, Portugal, 19-21 November 2015, Volume 2, pp. 757–768, 2015

\bibitem{ECardarelli} Elena Cardarelli, Lorenzo Sabattini, Valerio Digani, Cristian Secchi and Cesare Fantuzzi, ``Interacting with a Multi AGV System", 11th IEEE International Conference on
Intelligent Computer Communication and Processing, ICCP 2015, pp. 263-267, 2015

\bibitem{AKar} Aniket K. Kar, Narendra K. Dhar, S. S. Farhad Nawaz, Rashi Chandola, Nishchal K. Verma, ``Automated guided vehicle navigation with obstacle avoidance in normal and guided environments", 11th International Conference on Industrial and Information Systems (ICIIS), pp. 77-82, 2016

\bibitem{SDas} Suman Kumar Das, M. K. Pasan, ``Design and Methodology of Automated Guided Vehicle-A Review", IOSR Journal of Mechanical and Civil Engineering (IOSR-JMCE), pp. 29-35, 2016

\bibitem{ABirari} Akshay Birari, Amit Kharat, Purva Joshi, Rahul Pakhare, Unmesh Datar, Vaibhav Khotre, ``Velocity Control of Omni Drive Robot using PID Controller and Dual Feedback", IEEE First International Conference on Control, Measurement and Instrumentation (CMI), pp. 295-299, 2016

\bibitem{SLu} Shaoping Lu, Chen Xu, Ray Y. Zhong, Lihui Wang, ``A RFID-enabled positioning system in automated guided vehicle for smart factories", Journal of Manufacturing Systems, Vol. 44, Part 1, pp. 179-190, 2017

\bibitem{AGonzalez} Alberto Aguilar-Gonzalez, Camilo Lozoya, Luis Orona,  Salvador Romo, Armando Roman-Flores, ``Campus Kart: An Automated Guided Vehicle to Teach Using a Multidisciplinary Approach", IEEE Revista Iberoamericana de Tecnologias del Aprendizaje, Vol. 12, No.4, pp. 199-207, 2017

\bibitem{JBacik} J\`{a}n Ba\u{c}\'{i}k, Frankti\u{s}ek \u{D}urovsk\'{y}, Milan Biro\u{s}, Karol Kyslan, Daniela  Perdukov\'{a}, Sanjeevikumar Padmanavban, ``Pathfinder—Development of Automated Guided Vehicle for Hospital Logistics", IEEE Access, Vol. 5, pp. 26892-26900, 2017


\bibitem{JQian} Jun Qian, Bin Zi, Daoming Wang, Yangang Ma, Dan Zhang, ``The Design and Development of an Omni-Directional Mobile Robot Oriented to an Intelligent Manufacturing System", Sensors, Vol. 17, 2017

\bibitem{VPatil} Virendra Patil, Bhatwadekar S. G., ``AUTOMATED GUIDED VEHICLE SYSTEM", International Research Journal of Engineering and Technology (IRJET), 2018

\bibitem{JWeng} Jian-Fu Weng, Kuo-Lan Su, ``Development of a SLAM based automated guided vehicle", Journal of Intelligent \& Fuzzy Systems, pp. 1–13, 2018

\bibitem{SIto} Seigo Ito, Shigeyoshi Hiratsuka, Mitsuhiko Ohta, Hiroyuki Matsubara, Masaru Ogawa, ``Small Imaging Depth LIDAR and DCNN-Based Localization for Automated Guided Vehicle", Sensors, Vol. 18, 2018

\bibitem{JTheunissen} Jacobus Theunissen, Hang Xu,  Ray Y Zhong, Xun Xu, ``Smart AGV System for Manufacturing Shopfloor in the Context of Industry 4.0", 25th International Conference on Mechatronics and Machine Vision in Practice (M2VIP), 2018

\bibitem{DBore} Dipak Bore, Amit Rana, Nilima Kolhare, Ulhas Shinde, ``Automated Guided Vehicle Using Robot Operating Systems", Third International Conference on Trends in Electronics and Informatics (ICOEI), pp. 819-822, 2019

\bibitem{SAkutsu} Susumu Akutsu, Makoto Tanaka, ``Automated Guided Vehicle", US 2019/0171219 A1, United States Patent and Trademark Office, Jun. 6, 2019

\bibitem{HOsawa} Hiroki Osawa, Masahiro Sakakibara, Takahiro Ueno, ``Cargo Transport System and Automated Guided Vehicle", US 2019/0384280 A1, United States Patent and Trademark Office, Dec. 19, 2019

\bibitem{ZQian} Zhikang Qian, Qiyi Guo, Minh-Trien Pham, Wei Li, ``Design of a Low Power Consumption Control System of Permanent Magnet Synchronous Motor for Automated Guided Vehicle", 22nd International Conference on Electrical Machines and Systems (ICEMS), 2019

\bibitem{YSun} Yunlong Sun, Lianwu Guan, Zhanyuan Chang, Chuanjiang Li, Yanbin Gao, ``Design of a Low-Cost Indoor Navigation System for Food Delivery Robot Based on Multi-Sensor Information Fusion", Sensors, Vol. 19, 2019

\bibitem{MBoscarato} Matteo Boscarato, ``Development of Path Planning Algorithms for AGVs in the Primary Aluminium Industry", Master Thesis, Universit\'{a} Degli Studi Di Padova, 2019

\bibitem{BReddy} Bhusapalli Dhamodar Reddy, A. A. Nippun Kumaar, ``Indoor Mobile Robot Path Planning Using QR Code", International Conference on Communication, Computing and Electronics Systems, Lectures Notes in Electrical Engineering, Vol. 637, pp. 681-695, 2019

\bibitem{BPutra} B E Putra, A Z Arfianto, L Subiyanto, Z M A Putra, M K Hasin, D A Utari, M B Rahmat, D Hidayat, M Taali, A Y Lusiandri, V Y P Ardhana, ``Multi Automated Guided Vehicle (AGV) cardboard carrier using wireless communication", IOP Conf. Series: Earth and Environmental Science, Vol. 340, 2019

\bibitem{HYoshitake} Hiroshi Yoshitake, Ryote Kamoshida, Yoshikazu Nagashima, ``New Automated Guided Vehicle System using Real-time Holonic Scheduling for Warehouse Picking", IEEE Robotics and Automation Letters, pp. 1-8, 2019

\bibitem{SKim} Sungkwan Kim, Hojun Jin, Minah Seo, Dongsoo Har, ``Optimal Path Planning of Automated Guided Vehicle using Dijkstra Algorithm under Dynamic Conditions", 2019 7th International Conference on Robot Intelligence Technology and Applications (RiTA), pp. 231-236, 2019

\bibitem{JLuo} Jiliang Luo, Yaxin Wan, Weimin Wu, Zhiwu Li, ``Optimal Petri-Net Controller for Avoiding Collisions in a Class of Automated Guided Vehicle Systems". IEEE Transactions on Intelligent Transportation Systems, pp. 1–12, 2019

\bibitem{MSeptyan} Mamat Septyan, Trihastuti Agustinah, ``Trajectory Tracking Automated Guided Vehicle Using Fuzzy Controller", 2019 International Conference of Artificial Intelligence and Information Technology (ICAIIT), pp. 169-174, 2019


\bibitem{WZou} Wen-Qiang, Quan-Ke Pan, M. Faith Tasgetiren, ``An Effective Discrete Artificial Bee Colony Algorithm for Scheduling an Automatic-Guided-Vehicle in a Linear Manufacturing Workshop", IEEE Access, Vol. 8, pp. 35063-35076, 2020

\bibitem{FDebrouwere} M. De Ryck, M. Versteyhe, F. Debrouwere, ``Automated guided vehicle systems, state-of-the-art control algorithms and techniques", Journal of Manufacturing Systems, Vol. 54, pp. 152-173, 2020

\bibitem{AEzzy} Abbas Shabbir Ezzy, Farhan Zafar Khan, Moiz Akram, Janib Agha,  Atif Saeed, ``Automated Logistic Systems: Needs and Implementation", 3C Tecnolog\`{i}a Glosas de innovaci\'{o}n aplicadas a la pyme, pp. 27-45, 2020

\bibitem{DNaga} Dr.D.Nagarathinam, ``Current Status about Automated Guided Vehicle and Their Advantages and Application", International Journal of Recent Trends in Engineering \& Research, pp. 10-16, 2020

\bibitem{MQuemelli} M. B. Quemelli, A. S. Brand\~{a}o, ``Handling and pushing objects using unmanned guided vehicles", Robotics and Computer Integrated Manufacturing, Vol. 63, 2020

\bibitem{KShariatmadar} M. De Ryck, M. Versteyhe, K. Shariatmadar,  ``Resource management in decentralized industrial Automated Guided Vehicle systems", Journal of Manufacturing Systems, Vol. 54, pp. 204-214, 2020

\bibitem{ZNing} Zhixiong Ning, Xin Wang, Jun Wang, Huafeng Wen, ``Vehicle pose estimation algorithm for parking automated guided vehicle", International Journal of Advanced Robotic Systems, pp. 1-11, 2020

\bibitem{CLee} Chen Wei Lee, Wai Peng Wong, Joshua Ignatius, Amirah Rahman, Ming-Lang Tseng, ``Winner determination problem in multiple automated guided vehicle considering cost and flexibility", Computers \& Industrial Engineering, Vol. 142, 2020

\end{thebibliography}

\newpage


\chapter*{Websites}

\begin{itemize}
\small
\item \url{https://www.autodesk.com/education/free-software/fusion-360-for-educational-institutions}\label{fusion360}

\item \url{https://www.autodesk.in/products/eagle/overview}\label{eagle}

\item \url{https://www.arduino.cc/en/Main/Software}\label{arduinoide}

\item \url{https://docs.python.org/3/library/idle.html}\label{pythonidle}

\item \url{https://www.raspberrypi.org/downloads/raspbian/}\label{raspbian}

\item \url{https://github.com/EdjeElectronics/TensorFlow-Lite-Object-Detection-on-Android-and-Raspberry-Pi}\label{edjeelectronics}

\item \url{https://www.anaconda.com/}

\item \url{https://www.tensorflow.org/}\label{tensorflow}

\item \url{https://www.pcbway.com/}

\item \url{https://robu.in/}

\item \url{https://www.zdnet.com/article/what-is-the-raspberry-pi-4-everything-you-need-to-know-about-the-tiny-low-cost-computer/}

\item \url{https://www.wikipedia.org/}

\item \url{https://www.techopedia.com/}

\item \url{https://www.tutorialspoint.com/}

\item \url{https://medium.com/}

\item \url{https://internetofthingsagenda.techtarget.com/}

\end{itemize}